\vspace{-0.5cm}The X-shooter GTO sample of GRB afterglow and host Galaxy spectra

### 2016-09-24 document/XSGRB_sample.tex
Small edit

	\subsection{GRB100724A (z = 1.288)}
	The data presented here also formed the basis of GCN \#
	10971\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/10971.gcn3}}. 
	The spectrum has not otherwise been published previously. The observations were
	carried out in RRM starting 11 min after the GRB trigger. 
	See section \ref{RRM}, for a description of the RRM scheme.
	Absorption lines from several ionic species are detected in the afterglow continuum at a common redshift
	of $z = 1.288$.

>>>>

	\subsection{GRB100724A* (z = 1.288)}
	The data presented here also formed the basis of GCN \#
	10971\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/10971.gcn3}}. 
	The spectrum has not otherwise been published previously. The observations were
	carried out in RRM starting 11 min after the GRB trigger. 
	See section \ref{RRM}, for a description of the RRM scheme.
	Absorption lines from several ionic species are detected in the afterglow continuum at a common redshift
	of $z = 1.288$. This burst is not a part of the statistical sample.
